\chapter{What is a Proof?}
\section{Propositions}
\begin{definition}
    A \note{proposition} is a statement (communication) that is either
    true or false.
\end{definition}
\begin{claim}
    $\forall$ $n \in \mathbb{N}$, $p::=n^2+n+41$ is prime
\end{claim}
\boldText{Question: } Is this claim true or false?
\begin{claim}
    No polynomial with integer coefficients can map all nonnegative numbers
    into primes, unless it's a constant.
\end{claim}
\boldText{Question: } Is this true or false?
\begin{claim}[Euler's Conjecture]
    $\forall a,b,c,d \in \mathbb{Z^{+}}$. $a^4 + b^4 + c^4 \neq d^4$
\end{claim}
\begin{claim}
    $313(x^3 + y^3) = z^3$ has no solution when $x,y,z \in \mathbb{Z^{+}}$
\end{claim}
\begin{claim}[Four Color Theorem]
    Every map can be colored with $4$ colors so that adjacent regions have different
    colors.
\end{claim}
\begin{claim}[Fermat's Last Theorem]
    $\forall a,b,c \in \mathbb{Z^{+}}\;\forall n > 2, n \in \mathbb{Z}$. $a^n + b^n \neq c^n$
\end{claim}
\begin{claim}[Goldbach]
    Every even integer greater than $2$ is the sum of two primes.
\end{claim}

\section{Predicates}
\begin{definition}
    A \note{predicate} is a proposition whose truth depends on the value of one
    or more variables.
\end{definition}
If $P$ is a predicate, then $P(n)$ is either \note{true} or \note{false}, depending on
the value of $n$.

\section{The Axiomatic Method}
\begin{definition}
    A \note{proof} is a sequence of logical deductions from a set of axioms
    and previous proved propositions that concludes with the proposition in question.
\end{definition}
\begin{itemize}
    \item \note{Theorems}
    \item \note{Lemma}
    \item \note{Corollary} 
\end{itemize}
$\Rightarrow$ Axiomatic Method