\chapter{The Well Ordering Principle (WOP)}

\begin{pr}
    We shall prove the following statement,
    \begin{lemPr}
        Every amount of postage that can be assembled using only $10$ cent
        and $15$ cent stamps is divisible by $5$.
    \end{lemPr}

    \begin{proof}
        Let the notation "$j\left|\right.k$" indicate the integer $j$
        is a divisor of integer $k$, and let $S(n)$ mean that exactly $n$ cents
        postage can be assembled using only $10$ and $15$ cent stamps. Then
        the proof shows that
        \begin{equation} \label{statement:pr1}
            S(n) \quad \text{IMPLIES} \quad 5 \left|\right. n, \qquad \text{for all nonnegative integers n.}
        \end{equation}
        Let $C$ be the set of \note{counterexamples} to (\ref{statement:pr1}), namely
        \begin{equation*}
            C ::= \left\{ n \left|\right. S(n) \ \text{DOES NOT IMPLY} \ 5 \left|\right. n \ \text{for some} \ n \in S(n) \right\}
        \end{equation*}
        Assume for the purpose of obtaining a contradiction that $C \neq \emptyset$.
        By WOP, there exists a smallest $m \in C$. This $m$ must be positive
        because $5 \left|\right. 0$.
        \beautyBr
        But if $S(m)$ holds and $m$ is positive, then $S(m - 10)$ or $S(m - 15)$
        must hold, because for all positive $m = 10i + 15j$ for either $i > 0$ or $j > 0$; if
        $i > 0$, $(m - 10) \in S(m - 10)$; if $j > 0$, $(m - 15) \in S(m - 15)$.
        \beautyBr
        So suppose $S(m - 10)$ holds. Then $5 \left|\right. m - 10$, because $(m - 10) \notin C$.
        \beautyBr
        But this means that $5 \left|\right. m$, contradicting the fact that
        $m$ is a counterexample.
        \beautyBr
        Next, if $S(m - 15)$ holds, we arrive at a contradiction the same way.
        \beautyBr
        Since we get a contradiction in both cases, we conclude that $C = \emptyset$,
        which proves that $(\ref{statement:pr1})$ holds.
    \end{proof}
\end{pr}

\begin{pr}
    Note that $1 \in C$. This means that $0 < m \leq 1$. Since $m \in \ms{N}$,
    $m = 1$. However, $F(m - 2) = F(-1)$ does not exist: the proof is bogus.
\end{pr}

\begin{pr}
    WOP cannot be applied on the set of rational numbers. Indeed, the set
    of positive rational numbers have no minimum element.
\end{pr}

\begin{pr}
    We shall prove by contradiction on the number of summands. Let $\ms{C}$
    be the set of nonnegative integers of summands which do not satisfy
    the original equation, that is,
    \begin{equation*}
        \ms{C} = \left\{ n \in \ms{N} \ \left| \ \sum_{k=0}^{n} k^2 \neq \dfrac{n(n + 1)(2n+1)}{6} \right. \right\}
    \end{equation*}
    Assume for the sake of contradiction that $\ms{C} \neq \emptyset$.
    By WOP, there exists a smallest nonnegative integer $c_0 \in \ms{C}$.
    Since the equation is satisfied for $n = 0$, $c_0 > 0$. Therefore,
    $c_0 - 1$ is a nonnegative integer, and since $c_0 - 1 \notin \ms{C}$, we have,
    \begin{equation*}
        \sum_{k=0}^{c_0-1} k^2 = \dfrac{c_0(c_0-1)(2c_0-1)}{6}
    \end{equation*}
    Adding $c_0^2$ to both sides, we get
    \begin{align*}
        \sum_{k=0}^{c_0} k^2 &= \dfrac{c_0(c_0-1)(2c_0-1)}{6} + c_0^2 \\
        &= \dfrac{c_0(c_0-1)(2c_0-1) + 6c_0^2}{6} \\
        &= \dfrac{c_0\left[(c_0-1)(2c_0-1) + 6c_0\right]}{6} \\
        &= \dfrac{c_0\left[2c_0^2 + 3c_0 + 1\right]}{6} \\
        &= \dfrac{c_0\left[2c_0(c_0 + 1) + (c_0 + 1)\right]}{6} \\
        &= \dfrac{c_0(c_0 + 1)(2c_0 + 1)}{6}
    \end{align*}
    which contradicts the fact that $c_0 \in \ms{C}$.
\end{pr}

\begin{pr}
    Define $S$ a set of positive integers $c$ such that,
    \begin{equation*}
        S := \left\{ c \in \ms{N} \ \left| \ \exists a,b \in \ms{N} \text{ such that } 4a^3 + 2b^3 = c^3 \right. \right\}
    \end{equation*}
    Assume by contradiction that $S \neq \emptyset$. By WOP, there exists a smallest $c_0 \in S$.
    Fix the tuple $(a_0, b_0, c_0)$ to be the solution to the equation.
    \beautyBr

    By LHS, $c_0^3$ is even. Therefore, $c_0$ is even. Let $c_0 = 2k$ for some positive integer $k$. Then,
    \[
        4a_0^3 + 2b_0^3 = 8k^3 \implies 2a_0^3 + b_0^3 = 4k^3
    \]
    which implies that
    \[
        2a_0^3 + b_0^3 \text{ is divisible by } 4.
    \]
    We shall prove that $a_0$ must be even.
    Assume that $a_0$ is odd. Then $a_0^3$ is odd. This means
    $a_0^3 = 2m + 1$ for some nonnegative integer $m$, which implies,
    \[
        2a_0^3 = 4m + 2
    \]
    So a division of $2a_0^3$ by $4$ has a remainder of $2$.
    \beautyBr

    We shall prove that $b_0^3$ cannot have a remainder of $2$. Suppose
    $b_0$ is even. Then $b_0^3$ is even, and a division of $b_0^3$ by $4$ has a remainder of $0$.
    Suppose $b_0$ is odd. Then
    \[
        b_0^3 = (2n + 1)^3 = 8n^3 + 12n^2 + 6n + 1 = 4(2n^3 + 3n^2 + n) + 2n + 1
    \]
    for some nonnegative integer $n$. So a division of $b_0^3$ by $4$
    has a remainder of either $1$ or $3$.
    \beautyBr

    However, this means that $2a_0^3 + b_0^3$ cannot be divisible by $4$: therefore, $a_0$ must be even.
    \beautyBr

    Since $2a_0^3 + b_0^3$ is divisible by $4$, $b_0^3$ must be even, and
    therefore $b_0$ must be even. It follows that the tuple $(a_0, b_0, c_0)$
    is all even.
    \beautyBr

    Let $a_0 = 2a_1$, $b_0 = 2b_1$, and $c_0 = 2c_1$ for some positive integers $a_1, b_1, c_1$.
    Then,
    \begin{IEEEeqnarray*}{rCl}
        4a_0^3 + 2b_0^3 &=& c_0^3 \\
        4(2a_1)^3 + 2(2b_1)^3 &=& (2c_1)^3 \\
        4(8a_1^3) + 2(8b_1^3) &=& 8c_1^3 \\
        4a_1^3 + 2b_1^3 &=& c_1^3
    \end{IEEEeqnarray*}
    which contradicts the fact that $c_0$ is the smallest element in $S$.
\end{pr}

\begin{pr}
    You are given a series of envelopes, respectively containing $1,2,4,\ldots,2^{m}$ dollars.\\
    Define
    \begin{propertym}
        \textbf{Property \textsl{m}}: For any nonnegative integer less than $2^{m+1}$
        , there is a selection of envelopes whose contents add up to \textsl{exactly}
        that number of dollars.
    \end{propertym}
    Use the Well Ordering Principle (WOP) to prove
    that Property $m$ holds for all nonnegative integers $m$.
\end{pr}

\begin{solution}
    Begin solution here \ldots
\end{solution}
